Psyc 601 Multivariate Statistics Project

### 2013-08-16 writeups/proposal/proposal.tex
foo
Former-commit-id: d25ad90b48b4595a355e158baf4107201f93d065 [formerly 6f0f2e4d379526fd73a8ea12538bfd9d34d7013d]
Former-commit-id: 574e885413b29591d664761c0375847bf3754a53
foo
Former-commit-id: 73f94630abd97f5a6e20461eb6ddedcc9282fdf2 [formerly 1df978033bac6518a474b5472a4c670dd5cbae29]
Former-commit-id: 811f713786e599ca65dcdfcc26fd6f20a8a62288

@@

TODO: Challenging domain due to time constraints on information. \cite{Bauer2012}

@@

TODO: Summarize and \cite{Bennett2007}

@@

TODO: \cite{Kuo2011}

>>>>

\AtEveryBibitem{\clearfield{doi}}

\AtEveryBibitem{
  \ifentrytype{misc}{}{
    \clearfield{url}
  }
}

@@

FIXME: Fix cite for Bauer2012
TODO: Challenging domain due to time constraints on information. \cite{Bauer2012}

@@

FIXME: Fix cite for Bennett2007
TODO: Summarize and \cite{Bennett2007}

@@

TODO: \cite{Kuo2011}
FIXME: cite recent paper
FIXME: cite tex.stackexchange.org as a hashtag suggestion tool
